### 2015-05-07 Workshop2015/camera-ready/introduction.tex
mostly spell checking

To better understand our problem, consider a massive open online course system (MOOC) where users produce and consume content according to the geographic area and the expertise of participants. 
Producers are characterized according to their location, the type and topic of  content  they can provide, the access conditions (e.g. cost, inscription, or exchange unit), and the time window in which they can produce content. 
Consumers are characterized by their location, their interests  during a certain interval of time, the maximum total cost they are ready to pay consuming content, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content. Both producers and consumers have subscriptions to different cloud providers for dealing with content storage, processing and exchange.
The MOOC  aims at being privacy respectful of the producers and consumers participating in courses.
 Providers  and consumers can ask to minimize the transfer of personal data  when they share/consume content.  According to the level of trust associated to data providers, the MOOC can use privacy preserving technics to let users share content anonymously  (Constraint1). Furthermore,  data providers can  also wish to give restricted data access credentials w.r.t. to their  trust level, when their data are used  within  an integration process (Constraint 2).

@@

This paper is organized as follows. Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes in cloud environments. Section \ref{sec:incremental} gives an overview of our approach and highlights the need of new kind of SLA to conduct the integration process. Section \ref{sec:derivedSla}, \ref{sec:queryRew} and \ref{sec:queryProcessOpt} give an idea of the main steps of our proposal.  Finally section  \ref{sec:conclusions} concludes the paper and discusses future work.

>>>>

To better understand our problem, consider a massive open online course system (MOOC) where users produce and consume content according to the geographic area and the expertise of participants. 
Producers are characterized according to their location, the type and topic of  content  they can provide, the access conditions (e.g. cost, inscription, or exchange unit), and the time window in which they can produce content. 
Consumers are characterized by their location, their interests  during a certain interval of time, the maximum total cost they are ready to pay consuming content, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content. Both producers and consumers have subscriptions to different cloud providers for dealing with content storage, processing and exchange.
The MOOC  aims at being privacy respectful of the producers and consumers participating in courses.
 Providers  and consumers can ask to minimize the transfer of personal data  when they share/consume content.  According to the level of trust associated to data providers, the MOOC can use privacy preserving techniques to let users share content anonymously  (Constraint1). Furthermore,  data providers can  also wish to give restricted data access credentials w.r.t. to their  trust level, when their data are used  within  an integration process (Constraint 2).

@@

This paper is organized as follows. Section \ref{sec:relWork} presents related works that address SLA modeling, integration and SLA guided data management processes in cloud environments. Section \ref{sec:incremental} gives an overview of our approach and highlights the need of new kind of SLA to conduct the integration process. Section \ref{sec:derivedSla}, \ref{sec:queryRew} and \ref{sec:queryProcessOpt} give an idea of the main steps of our proposal.  Finally section  \ref{sec:conclusions} concludes the paper and discusses future work.
